Carbonate chemistry at Ny-Ålesund

### 2021-10-25 awipev-CO2.Rmd
Revised lm2

#################### Function RMSE for model 2 regression root mean square error
#test <- readr::read_csv(file="test_file")
lm2 <- function(data = NULL, x, y) {
  col_x <- eval(substitute(x), data)
  col_y <- eval(substitute(y), data)
  col_x <- x
  col_y <- y
fit <- lmodel2(col_y ~ col_x, nperm = 99)
  intercept_MA <- fit$regression.results[2,2]
  slope_MA <- fit$regression.results[2,3]
  intercept_OLS <- fit$regression.results[1,2]
  slope_OLS <- fit$regression.results[1,3]
  predicted <- intercept_OLS + col_x * slope_OLS
  error <- col_x - predicted
  my_list <- list(intercept_MA = intercept_MA, 
                  slope_MA = slope_MA,
                  intercept_OLS = intercept_MA, 
                  slope_OLS = slope_MA,
                  rmse = sqrt(mean(error^2, na.rm=TRUE)))
  return(my_list)
}

@@

```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
lm <- lm2(x = d_all$sal_insitu_ctd_9m, y = d_all$sal_fb)
p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
  geom_point( aes(color=factor(monthd))) + 
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + #
  coord_fixed(ratio = 1 )+
  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") + theme_bw()

>>>>

#################### Function RMSE for model 2 regression root mean square error
#test <- readr::read_csv(file="test_file")
lm2 <- function(data = NULL, x, y) {
  col_x <- eval(substitute(x), data)
  col_y <- eval(substitute(y), data)
  col_x <- x
  col_y <- y
fit <- lmodel2(col_y ~ col_x, nperm = 99)
  intercept_MA <- fit$regression.results[2,2]
  slope_MA <- fit$regression.results[2,3]
  intercept_OLS <- fit$regression.results[1,2]
  slope_OLS <- fit$regression.results[1,3]
  predicted <- intercept_OLS + col_x * slope_OLS
  error <- col_x - predicted
  rsquare <- fit$rsquare
  P.param <- fit$P.param
  my_list <- list(intercept_MA = intercept_MA, 
                  slope_MA = slope_MA,
                  intercept_OLS = intercept_MA, 
                  slope_OLS = slope_MA,
                  rsquare = rsquare,
                  P = P.param,
                  rmse = sqrt(mean(error^2, na.rm=TRUE)))
  return(my_list)
}

@@

```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
lm <- lm2(x = d_all$sal_insitu_ctd_9m, y = d_all$sal_fb)
p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
  geom_point( aes(color=factor(monthd))) + 
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(lm$rsquare, 3),
                     "; Intercept =", signif(lm$intercept_MA, 3),
                     "; Slope =", signif(lm$slope_MA, 3),
                     "; P =", signif(lm$P, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + #
  coord_fixed(ratio = 1 )+
  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") + theme_bw()
